ShabbyPages: A Recipe for Repeatable, Synthetic, Modern Document Images

### 2023-01-23 paper/paper.tex

\title{ShabbyPages: A Recipe for Repeatable, Synthetic, Modern Document Images}
\author{Alexander Groleau\inst{1,2} \and
  Kok Wei Chee\inst{1} \and
  Stefan Larson\inst{3} \and
  Jonathan Boarman\inst{1} \and
  Samay Maini\inst{1}}

\authorrunning{A. Groleau et al.}

\institute{Sparkfish LLC (\email{augraphy@sparkfish.com})
  \and
  Left Associates LLC (\email{research@left.associates})
  \and
  Vanderbilt University}

@@

\subsection{Features}
Modern artificial neural networks produce a latent representation of their training data, a space from which outputs are sampled. In deep networks, these representations live within multiple layers, each of which corresponds to a feature of the input data. Document images are a particularly interesting category, as the data within the documents each picture represents is itself frequently multi-modal; the document may contain an image and its description, a table with statistics, multiple regions of structured and formatted text, and even other documents, making their internal representations by neural networks often quite complicated.\\

Networks with a wider variety of latent representations frequently perform better when generalizing their learned functions to other tasks. Procuring a large-enough volume of robust-enough training data is paramount. Several sets of such images exist, many intended for processing by deep neural nets; Table 1 below contains a comparison of some of the key hyperproperties of the ShabbyPages set compared with other popular document image datasets.\\

@@

\subsubsection{NoisyOffice}
The NoisyOffice database \cite{ref_NoisyOffice} contains a very low 4 base images, 2 types of font, 3 font sizes, and 4 types of noise, for a total of 72 unique images. The groundtruth images were produced in a standard word processor, with the simulated noisy images produced by first adding noise to a blank sheet of paper, storing that as a background image after digital scanning, then overlaying the foreground text onto the noisy background texture. An additional set of real NoisyOffice images was produced, where the foreground text was printed on blank white sheets, the results of which were physically augmented by the introduction of footprints, coffee stains, wrinkles, and folds.\\

@@

The images exhibit poor fidelity with what we can imagine their originals to have been, contain substantial noise, and many were scanned at around 100 pixels per inch, quite a low resolution for documents. None of the images in the CDIP set come with groundtruths.\\

@@

\subsection{Tobacco800}
Tobacco800, like RVL-CDIP, is a subset of the Complex Document Image Processing collection, containing images of documents originally internal to tobacco companies, and released under the Tobacco Master Settlement Agreement. The corpus is composed of 1290 images, gathered and scanned at different times and by different devices. Several of the images in this set are consecutively-numbered pages, increasing the set's utility for certain image analysis tasks \cite{ref_Tobacco800}. Document images in this set vary from from 150 to 300 DPI with dimensions between 1200 pixels wide and 2500 pixels tall on the low end and 1600 by 3200 on the high.\\

@@

\subsection{ShabbyPages Compared}
Supervised learning tasks require labeled training data, called the ground truth. Much of the world's data does not come with labels, which instead must be created by humans in some fashion. In Table 1, we indicated that NoisyOffice was the only other groundtruthed dataset we examined. This isn't strictly true: there are projects to add some types of groundtruth to RVL-CDIP \cite{ref_goldmann}, \cite{ref_zenodo} and Tobacco800 \cite{ref_tobacco800gt1}, \cite{ref_tobacco800gt2}, but the images in these sets were produced by real scans, without an accompanying original digital document. Conversely, NoisyOffice contains images of real scanned documents intended for validation, as well as their digital groundtruth and synthetic training image data.\\

@@

\subsection{Statistics}
ShabbyPages contains documents from multiple classes, which contain many types of information.\\

@@

\subsection{Limitations}
The ShabbyPages collection is a comprehensive entrant to the public datasphere, but with a relatively low starting document volume, makes some important omissions.\\

First, we arbitrarily selected 600 as the number of source documents. The number of final images of pages depends on this, and so is similarly arbitrary.\\

@@

\section{Experimentation with the ShabbyPages Set}
Binarization and denoising are two important techniques for the removal of unwanted data from images. Both approaches can be achieved by supervised learning of relationships between features of the input and output data. In this section, we train and compare several instances of the NAFNet \cite{ref_NAFNet} architecture as denoisers and binarizers, and evaluate these models' predictions on both the NoisyOffice and ShabbyPages datasets. The model was ``off-the-shelf'' — besides rigging up the training inputs, we made no alterations to the

\subsection{Motivation for Denoising}
Digital computation has enabled humanity to produce ever-growing amounts of both data and reasons to process it. Doing so is easiest when the data is free of unexpected outliers, the signal has less jitter, or when our aesthetic sensibilities aren't injured.\\

\subsection{Binarization}
In this section, we discuss results obtained by training a binarizing denoiser to both restore augmented images to their ground truths and to classify pixels as foreground.\\

@@

One instance of the model was trained on the SimulatedNoisyOffice corpus, while the other was trained on a subset of ShabbyPages, in both cases using the relevant ensemble-binarized groundtruths. As a test, these models were used to denoise and binarize both the NoisyOfficeReal dataset and a testing subset taken from ShabbyPages which does not overlap the training subset. Common image processing metrics were applied to the predictions made by each model, comparing these to the (preprocessed) groundtruths. The averages of each metric over all such predictions was taken; these are presented in Table 2.
\begin{table}[]
    \centering
    \caption{Image restoration performance between NoisyOffice-trained and ShabbyPages-trained NAFNet binarizing denoisers on cross-validation task}
    \scalebox{0.81}{
    \begin{tabular}{llll}
    \toprule
    \textbf{Training Set} & \textbf{Test Set} & \textbf{SSIM} & \textbf{RMSE} & \textbf{PSNR} \\
        \midrule
        \textsf{ShabbyPages} & \textsf{ShabbyPages} & \textsf{0.9255905809319086} & \textsf{2.987994328426575} & \textsf{39.29266235129017}\\
        \textsf{SimulatedNoisyOffice} & \textsf{RealNoisyOffice} & \textsf{0.9866020337197627} & \textsf{3.8045857559449296} & \textsf{36.73658388839052}\\
        \textsf{ShabbyPages} & \textsf{RealNoisyOffice} & \textsf{0.9465069385860134} & \textsf{3.2046770685272117} & \textsf{38.097843772060855}\\
        \textsf{SimulatedNoisyOffice} & \textsf{ShabbyPages} & \textsf{0.8105023745816482} & \textsf{5.38408321532059} & \textsf{34.56195157529838}\\
        \bottomrule
    \end{tabular}}
    \label{tab:binarization_results}
\end{table}

@@

Although the ShabbyPages-trained NAFNet predicted cleaned ShabbyPages images with a lower structural similarity score than the NoisyOffice-trained model predicted cleaned RealNoisyOffice images, the ShabbyPages model achieved superior performance on RMSE and PSNR. The ShabbyPages corpus contains a much higher feature diversity than NoisyOffice, so the lower SSIM score was not unexpected; local relationships between pixels were easier to encode for the NoisyOffice model, possibly because there are simply fewer relationships. The RMSE and PSNR results on the other hand indicate that the ShabbyPages-trained model learned to remove more noise with higher fidelity, and more accurately predicted foreground pixels than the NoisyOffice model. This discrepancy can partly be explained by the RealNoisyOffice corpus having been physically-noised as opposed to ShabbyPages' purely synthetic noise; small-scale features in the RealNoisyOffice testing data are not quite identical to the SimulatedNoisyOffice training inputs, while both the training and testing data taken from ShabbyPages was constructed by the same means. In the latter case, the \textit{diversity} of the ShabbyPages data is much higher (TODO: add diversity score info), and this instance of the NAFNet may have been able to generalize over noise types better than the NoisyOffice-trained network with its lower training diversity.\\

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_Kaggle}
  https://www.kaggle.com/datasets
\bibitem{ref_HuggingFaceHub}
  {https://huggingface.co/datasets}
\bibitem{ref_RDCL2019}
{Christian Clausner, RDCL2019 Competition Dataset (Recognition of Documents with Complex Layouts) (RDCL2019) ,1,ID:RDCL2019\_1,URL:https://tc11.cvc.uab.es/datasets/RDCL2019_1}

\bibitem{ref_Tobacco800}
{David Doermann, Tobacco 800 Dataset (Tobacco800) ,1,ID:Tobacco800_1,URL:https://tc11.cvc.uab.es/datasets/Tobacco800_1}

\bibitem{ref_icdar}
{Harold Mouchère, ICDAR 2019 Competition on Recognition of Handwritten Mathematical Expressions and Typeset Formula Detection (ICDAR2019-CROHME-TDF) ,1,ID:ICDAR2019-CROHME-TDF\_1,URL:https://tc11.cvc.uab.es/datasets/ICDAR2019-CROHME-TDF_1}

\bibitem{ref_NoisyOffice}
{Castro-Bleda, MJ.; España Boquera, S.; Pastor Pellicer, J.; Zamora Martínez, FJ. (2020). The NoisyOffice Database: A Corpus To Train Supervised Machine Learning Filters For Image Processing. The Computer Journal. 63(11):1658-1667. https://doi.org/10.1093/comjnl/bxz098}

\bibitem{ref_RVL-CDIP}
  @article{DBLP:journals/corr/HarleyUD15,
  author    = {Adam W. Harley and
               Alex Ufkes and
               Konstantinos G. Derpanis},
  title     = {Evaluation of Deep Convolutional Nets for Document Image Classification
               and Retrieval},
  journal   = {CoRR},
  volume    = {abs/1502.07058},
  year      = {2015},
  url       = {http://arxiv.org/abs/1502.07058},
  eprinttype = {arXiv},
  eprint    = {1502.07058},
  timestamp = {Mon, 13 Aug 2018 16:48:54 +0200},
  biburl    = {https://dblp.org/rec/journals/corr/HarleyUD15.bib},
  bibsource = {dblp computer science bibliography, https://dblp.org}
}

\bibitem{ref_NoisyOfficeDatabase}
{F. Zamora-Martinez, S. España-Boquera and M. J. Castro-Bleda, Behaviour-based Clustering of Neural Networks applied to Document Enhancement, in: Computational and Ambient Intelligence, pages 144-151, Springer, 2007.}

\bibitem{ref_UCIMLR}
{Dua, D. and Graff, C. (2019). UCI Machine Learning Repository [http://archive.ics.uci.edu/ml]. Irvine, CA: University of California, School of Information and Computer Science.}

\bibitem{ref_DocCreator}
  {Journet Nicholas, Visani Muriel, Mansencal Boris, Van-Cuong Kieu, Billy Antoine, DocCreator: A New Software for Creating Synthetic Ground-Truthed Document Images. J. Imaging 2017, 3, 62.}
\bibitem{ref_goldmann}
  {Pau Riba, Anjan Dutta, Lutz Goldmann, Alicia Fornes, Oriol Ramos, Josep LLados: "Table Detection in Invoice Documents by Graph Neural Networks", ICDAR, 2019.}
\bibitem{ref_zenodo}
  {Layout Analysis Groundtruth for the RVL-CDIP Dataset. Goldmann, Lutz. 10.5281/zenodo.3257319}
\bibitem{ref_tobacco800gt1}
  {Guangyu Zhu, Yefeng Zheng, David Doermann,and Stefan Jaeger. Multi-scale Structural Saliency for Signature Detection. In Proc. IEEE Conf. Computer Vision and Pattern Recognition (CVPR 2007), pp. 1‐8, 2007.}
\bibitem{ref_tobacco800gt2}
  {Guangyu Zhu and David Doermann. Automatic Document Logo Detection. In Proc. 9th Int. Conf. Document Analysis and Recognition (ICDAR 2007), pp. 864‐868, 2007.}

\bibitem{ref_NAFNet}
  @misc{https://doi.org/10.48550/arxiv.2204.04676,
  doi = {10.48550/ARXIV.2204.04676},
  url = {https://arxiv.org/abs/2204.04676},
  author = {Chen, Liangyu and Chu, Xiaojie and Zhang, Xiangyu and Sun, Jian},
  keywords = {Computer Vision and Pattern Recognition (cs.CV), FOS: Computer and information sciences, FOS: Computer and information sciences},
  title = {Simple Baselines for Image Restoration},
  publisher = {arXiv},
  year = {2022},
  copyright = {arXiv.org perpetual, non-exclusive license}
}

\end{thebibliography}
\end{document}

>>>>

\title{ShabbyPages: A Recipe for Repeatable, Synthetic, Modern Document Images}
%\author{Alexander Groleau\inst{1,2} \and
%  Kok Wei Chee\inst{1} \and
%  Stefan Larson\inst{3} \and
%  Jonathan Boarman\inst{1} \and
%  Samay Maini\inst{1}}
%
%\authorrunning{A. Groleau et al.}
%
%\institute{Sparkfish LLC (\email{augraphy@sparkfish.com})
%  \and
%  Left Associates LLC (\email{research@left.associates})
%  \and
%  Vanderbilt University}

\author{Anonymous ICDAR 2023 submission}

@@

\subsection{Features}
Modern artificial neural networks produce a latent representation of their training data, a space from which outputs are sampled.
In deep networks, these representations live within multiple layers, each of which corresponds to a feature of the input data.
Document images are a particularly interesting category, as the data within the documents each picture represents is itself frequently multi-modal; the document may contain an image and its description, a table with statistics, multiple regions of structured and formatted text, and even other documents, making their internal representations by neural networks often quite complicated.

Networks with a wider variety of latent representations frequently perform better when generalizing their learned functions to other tasks.
Procuring a large-enough volume of robust-enough training data is paramount.
Several sets of such images exist, many intended for processing by deep neural nets; Table 1 below contains a comparison of some of the key hyperproperties of the ShabbyPages set compared with other popular document image datasets.

@@

\subsubsection{NoisyOffice}
The NoisyOffice database \cite{ref_NoisyOffice} contains a very low 4 base images, 2 types of font, 3 font sizes, and 4 types of noise, for a total of 72 unique images.
The groundtruth images were produced in a standard word processor, with the simulated noisy images produced by first adding noise to a blank sheet of paper, storing that as a background image after digital scanning, then overlaying the foreground text onto the noisy background texture.
An additional set of real NoisyOffice images was produced, where the foreground text was printed on blank white sheets, the results of which were physically augmented by the introduction of footprints, coffee stains, wrinkles, and folds.

@@

The images exhibit poor fidelity with what we can imagine their originals to have been, contain substantial noise, and many were scanned at around 100 pixels per inch, quite a low resolution for documents.
None of the images in the CDIP set come with groundtruths.

@@

\subsection{Tobacco800}
Tobacco800, like RVL-CDIP, is a subset of the Complex Document Image Processing collection, containing images of documents originally internal to tobacco companies, and released under the Tobacco Master Settlement Agreement.
The corpus is composed of 1290 images, gathered and scanned at different times and by different devices.
Several of the images in this set are consecutively-numbered pages, increasing the set's utility for certain image analysis tasks \cite{ref_Tobacco800}.
Document images in this set vary from from 150 to 300 DPI with dimensions between 1200 pixels wide and 2500 pixels tall on the low end and 1600 by 3200 on the high.

@@

\subsection{ShabbyPages Compared}
Supervised learning tasks require labeled training data, called the ground truth.
Much of the world's data does not come with labels, which instead must be created by humans in some fashion.
In Table 1, we indicated that NoisyOffice was the only other groundtruthed dataset we examined.
This isn't strictly true: there are projects to add some types of groundtruth to RVL-CDIP \cite{ref_zenodo,ref_goldmann} and Tobacco800 \cite{ref_tobacco800gt2,ref_tobacco800gt1}, but the images in these sets were produced by real scans, without an accompanying original digital document.
Conversely, NoisyOffice contains images of real scanned documents intended for validation, as well as their digital groundtruth and synthetic training image data.

@@

\subsection{Statistics}
ShabbyPages contains documents from multiple classes, which contain many types of information.

@@

\subsection{Limitations}
The ShabbyPages collection is a comprehensive entrant to the public datasphere, but with a relatively low starting document volume, makes some important omissions.

First, we arbitrarily selected 600 as the number of source documents.
The number of final images of pages depends on this, and so is similarly arbitrary.

@@

\section{Experimentation with the ShabbyPages Set}
Binarization and denoising are two important techniques for the removal of unwanted data from images.
Both approaches can be achieved by supervised learning of relationships between features of the input and output data.
In this section, we train and compare several instances of the NAFNet \cite{ref_nafnet} architecture as denoisers and binarizers, and evaluate these models' predictions on both the NoisyOffice and ShabbyPages datasets.
The model was ``off-the-shelf''; besides rigging up the training inputs, we made no alterations to the

\subsection{Motivation for Denoising}
Digital computation has enabled humanity to produce ever-growing amounts of both data and reasons to process it.
Doing so is easiest when the data is free of unexpected outliers, the signal has less jitter, or when our aesthetic sensibilities aren't injured.

\subsection{Binarization}
In this section, we discuss results obtained by training a binarizing denoiser to both restore augmented images to their ground truths and to classify pixels as foreground.

@@

One instance of the model was trained on the SimulatedNoisyOffice corpus, while the other was trained on a subset of ShabbyPages, in both cases using the relevant ensemble-binarized groundtruths.
As a test, these models were used to denoise and binarize both the NoisyOfficeReal dataset and a testing subset taken from ShabbyPages which does not overlap the training subset.
Common image processing metrics were applied to the predictions made by each model, comparing these to the (preprocessed) groundtruths.
The averages of each metric over all such predictions was taken; these are presented in Table 2.

\begin{table}[]
    \centering
    \caption{Image restoration performance between NoisyOffice-trained and ShabbyPages-trained NAFNet binarizing denoisers on cross-validation task}
    \scalebox{0.81}{
    \begin{tabular}{llll}
    \toprule
    \textbf{Training Set} & \textbf{Test Set} & \textbf{SSIM} & \textbf{RMSE} & \textbf{PSNR} \\
        \midrule
        \textsf{ShabbyPages} & \textsf{ShabbyPages} & \textsf{0.9255905809319086} & \textsf{2.987994328426575} & \textsf{39.29266235129017}\\
        \textsf{SimulatedNoisyOffice} & \textsf{RealNoisyOffice} & \textsf{0.9866020337197627} & \textsf{3.8045857559449296} & \textsf{36.73658388839052}\\
        \textsf{ShabbyPages} & \textsf{RealNoisyOffice} & \textsf{0.9465069385860134} & \textsf{3.2046770685272117} & \textsf{38.097843772060855}\\
        \textsf{SimulatedNoisyOffice} & \textsf{ShabbyPages} & \textsf{0.8105023745816482} & \textsf{5.38408321532059} & \textsf{34.56195157529838}\\
        \bottomrule
    \end{tabular}}
    \label{tab:binarization_results}
\end{table}

@@

Although the ShabbyPages-trained NAFNet predicted cleaned ShabbyPages images with a lower structural similarity score than the NoisyOffice-trained model predicted cleaned RealNoisyOffice images, the ShabbyPages model achieved superior performance on RMSE and PSNR.
The ShabbyPages corpus contains a much higher feature diversity than NoisyOffice, so the lower SSIM score was not unexpected; local relationships between pixels were easier to encode for the NoisyOffice model, possibly because there are simply fewer relationships.
The RMSE and PSNR results on the other hand indicate that the ShabbyPages-trained model learned to remove more noise with higher fidelity, and more accurately predicted foreground pixels than the NoisyOffice model.
This discrepancy can partly be explained by the RealNoisyOffice corpus having been physically-noised as opposed to ShabbyPages' purely synthetic noise; small-scale features in the RealNoisyOffice testing data are not quite identical to the SimulatedNoisyOffice training inputs, while both the training and testing data taken from ShabbyPages was constructed by the same means.
In the latter case, the \textit{diversity} of the ShabbyPages data is much higher (TODO: add diversity score info), and this instance of the NAFNet may have been able to generalize over noise types better than the NoisyOffice-trained network with its lower training diversity.

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
 \bibliographystyle{splncs04}
 \bibliography{paper}

%\begin{thebibliography}{8}
%\bibitem{ref_Kaggle}
%  https://www.kaggle.com/datasets
%\bibitem{ref_HuggingFaceHub}
%  {https://huggingface.co/datasets}
%\bibitem{ref_RDCL2019}
%{Christian Clausner, RDCL2019 Competition Dataset (Recognition of Documents with Complex Layouts) (RDCL2019) ,1,ID:RDCL2019\_1,URL:https://tc11.cvc.uab.es/datasets/RDCL2019_1}
%
%\bibitem{ref_Tobacco800}
%{David Doermann, Tobacco 800 Dataset (Tobacco800) ,1,ID:Tobacco800_1,URL:https://tc11.cvc.uab.es/datasets/Tobacco800_1}
%
%\bibitem{ref_icdar}
%{Harold Mouchère, ICDAR 2019 Competition on Recognition of Handwritten Mathematical Expressions and Typeset Formula Detection (ICDAR2019-CROHME-TDF) ,1,ID:ICDAR2019-CROHME-TDF\_1,URL:https://tc11.cvc.uab.es/datasets/ICDAR2019-CROHME-TDF_1}
%
%\bibitem{ref_NoisyOffice}
%{Castro-Bleda, MJ.; España Boquera, S.; Pastor Pellicer, J.; Zamora Martínez, FJ. (2020). The NoisyOffice Database: A Corpus To Train Supervised Machine Learning Filters For Image Processing. The Computer Journal. 63(11):1658-1667. https://doi.org/10.1093/comjnl/bxz098}
%
%\bibitem{ref_RVL-CDIP}
%  @article{DBLP:journals/corr/HarleyUD15,
%  author    = {Adam W. Harley and
%               Alex Ufkes and
%               Konstantinos G. Derpanis},
%  title     = {Evaluation of Deep Convolutional Nets for Document Image Classification
%               and Retrieval},
%  journal   = {CoRR},
%  volume    = {abs/1502.07058},
%  year      = {2015},
%  url       = {http://arxiv.org/abs/1502.07058},
%  eprinttype = {arXiv},
%  eprint    = {1502.07058},
%  timestamp = {Mon, 13 Aug 2018 16:48:54 +0200},
%  biburl    = {https://dblp.org/rec/journals/corr/HarleyUD15.bib},
%  bibsource = {dblp computer science bibliography, https://dblp.org}
%}
%
%\bibitem{ref_NoisyOfficeDatabase}
%{F. Zamora-Martinez, S. España-Boquera and M. J. Castro-Bleda, Behaviour-based Clustering of Neural Networks applied to Document Enhancement, in: Computational and Ambient Intelligence, pages 144-151, Springer, 2007.}
%
%\bibitem{ref_UCIMLR}
%{Dua, D. and Graff, C. (2019). UCI Machine Learning Repository [http://archive.ics.uci.edu/ml]. Irvine, CA: University of California, School of Information and Computer Science.}
%
%\bibitem{ref_DocCreator}
%  {Journet Nicholas, Visani Muriel, Mansencal Boris, Van-Cuong Kieu, Billy Antoine, DocCreator: A New Software for Creating Synthetic Ground-Truthed Document Images. J. Imaging 2017, 3, 62.}
%\bibitem{ref_goldmann}
%  {Pau Riba, Anjan Dutta, Lutz Goldmann, Alicia Fornes, Oriol Ramos, Josep LLados: "Table Detection in Invoice Documents by Graph Neural Networks", ICDAR, 2019.}
%\bibitem{ref_zenodo}
%  {Layout Analysis Groundtruth for the RVL-CDIP Dataset. Goldmann, Lutz. 10.5281/zenodo.3257319}
%\bibitem{ref_tobacco800gt1}
%  {Guangyu Zhu, Yefeng Zheng, David Doermann,and Stefan Jaeger. Multi-scale Structural Saliency for Signature Detection. In Proc. IEEE Conf. Computer Vision and Pattern Recognition (CVPR 2007), pp. 1‐8, 2007.}
%\bibitem{ref_tobacco800gt2}
%  {Guangyu Zhu and David Doermann. Automatic Document Logo Detection. In Proc. 9th Int. Conf. Document Analysis and Recognition (ICDAR 2007), pp. 864‐868, 2007.}
%
%\bibitem{ref_NAFNet}
%  @misc{https://doi.org/10.48550/arxiv.2204.04676,
%  doi = {10.48550/ARXIV.2204.04676},
%  url = {https://arxiv.org/abs/2204.04676},
%  author = {Chen, Liangyu and Chu, Xiaojie and Zhang, Xiangyu and Sun, Jian},
%  keywords = {Computer Vision and Pattern Recognition (cs.CV), FOS: Computer and information sciences, FOS: Computer and information sciences},
%  title = {Simple Baselines for Image Restoration},
%  publisher = {arXiv},
%  year = {2022},
%  copyright = {arXiv.org perpetual, non-exclusive license}
%}
%
%
%\end{thebibliography}
\end{document}
